---
title: "Degen et al. (2020) replication - analysis"
output: rmarkdown::github_document
#output:
  #html_document: default
  #pdf_document: default
---

```{r import, include=FALSE}
setwd(dirname(rstudioapi::getSourceEditorContext()$path))

library(mongolite)
library(tidyverse)
library(jsonlite)
theme_set(theme_bw())

## for bootstrapping 95% confidence intervals
library(bootstrap)
theta <- function(x,xdata,na.rm=T) {mean(xdata[x],na.rm=na.rm)}
ci.low <- function(x,na.rm=T) {
  mean(x,na.rm=na.rm) - quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}
ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) - mean(x,na.rm=na.rm)}

# Analysis takes 1 file: 
  # 1. a .csv summary from Prolific of the experiment (prolific_export_XXXXXXXXX.csv)

# ... everything else is pulled from the DB via mongolite.

# It is IMPERATIVE that you .gitignore this file, as it contains identifying information of Prolific participants.

# Step 1: read in the file, downloaded from Prolific. (See ../screenshots/empirica_export.png for info on how to do this).

prolific_summary <- read_csv("../../data/EnglishPilot/identifyingInfo/prolific_export_60afcf977007299c487304c6.csv") %>%
  filter(started_datetime > "2021-06-02 00:00:00")
prolific_ids <- (prolific_summary %>% filter(status %in% c("AWAITING REVIEW", "APPROVED")))$participant_id
rm(prolific_summary)

# Step 2: read in the rounds and player info info from the Mongo database
# imported from a .gitignored .txt file

uname_pwd <- readLines("../../data/EnglishPilot/identifyingInfo/upwd")

# 'Rounds' contains the by-trial info

con <- mongo("rounds", url = sprintf("mongodb+srv://%s@cluster0.xizoq.mongodb.net/crossling-ref", uname_pwd))
d <- data.frame(con$aggregate()) %>%
  mutate(index = row_number())
con$disconnect()
rm(con)

rawD <- d

# 'Players' tells you which players played which games

con <- mongo("players", url = sprintf("mongodb+srv://%s@cluster0.xizoq.mongodb.net/crossling-ref", uname_pwd))
players <- data.frame(con$aggregate()) %>% 
  select(id, gameId) %>%
# We only want to focus on the games played by players with Prolific IDs recognized in file (1)
  filter(id %in% prolific_ids)
con$disconnect()
rm(con)

d <- d %>%
  filter(gameId %in% players$gameId)

# Step 3: do native language exclusions 

con <- mongo("player_inputs", url = sprintf("mongodb+srv://%s@cluster0.xizoq.mongodb.net/crossling-ref", uname_pwd))
player_info <- data.frame(con$aggregate()) %>% 
  filter(gameId %in% d$gameId) 
con$disconnect()
rm(con)

# Step 4: massage the data into something that looks like Degen et al.'s format

d <- cbind(d$gameId, d$X_id, d$data)

colnames(d)[1] <- "gameId"
colnames(d)[2] <- "X_id"

# (Manually) list games that featured a player who reported a native lang. other than English

excludeEnglish <- c()

d <- d %>%
  filter(!(gameId %in% excludeEnglish))

# Get the within-game round number

d <- d %>%
   group_by(group = cumsum(gameId != lag(gameId, default = first(gameId)))) %>%
   mutate(roundNumber = row_number()) %>%
   ungroup() %>%
   select(-group)

# Transform the speaker and listener chat into something more manageable, and return the item that the listener selected

directorFirstMessage <- c()
directorAllMessages <- c()
guesserAllMessages <- c()
nameClickedObj <- c()

d <- d %>%
  filter(!(chatLog == "NULL"))

for(i in seq(nrow(d))) {
  chat_temp <- d[i,]$gameChat[[1]]
  chat_temp <- cbind(chat_temp$text, chat_temp$player)
  colnames(chat_temp)[1] <- "text"
  
  chat_temp$text <- as.character(chat_temp$text)
  
  guesserChat <- chat_temp %>% filter(name == "Guesser")
  guesserAllMessages[i] <- paste(guesserChat$text, collapse = "__")
  
  directorChat <- chat_temp %>% filter(name == "Director")
  directorAllMessages[i] <- paste(directorChat$text, collapse = "__")
  
  if(nrow(directorChat) == 1) {
    directorFirstMessage[i] <- directorAllMessages[i]
    } else {
      directorFirstMessage[i] <- strsplit(directorAllMessages[i], split = "__", fixed = TRUE)[[1]][1]
    }
  
   # Return the item that the listener selected
  
    sel <- d[i,]$listenerSelection
    images<- data.frame(d[i,]$images)
    
    if(is.na(sel) || sel == "NONE") {
      nameClickedObj[i] <- sel 
    } else {
      nameClickedObj[i] <- (images %>% filter(id == sel))$name
    }

}

rm(chat_temp, guesserChat, directorChat, i, sel, images)

d <- cbind(d, directorAllMessages, directorFirstMessage, guesserAllMessages, nameClickedObj)

rm(directorAllMessages, directorFirstMessage, guesserAllMessages, nameClickedObj)

d <- d %>%
  mutate(correct = ifelse(d$target$id == listenerSelection, 1, 0))
```

#Sanity checks 

###Exclusions: 
```{r exclusions, echo=FALSE, warning=FALSE}
sprintf('Number of games excluded due to native lang: %d', length(excludeEnglish))
sprintf('Number of games after exclusions: %d', length(unique(d$gameId)) - length(excludeEnglish))
roundsPerGame <- d %>% group_by(gameId) %>% summarise(n = n())
sprintf('Avg. of rounds per game (should be exactly 72): %f', mean(roundsPerGame$n))
print("Rounds per game:")
roundsPerGame


excludeIncomplete <- (roundsPerGame %>% filter(n < 72))$gameId

# we can exclude incomplete games if we want... but Degen et al. 2020 do not.
d <- d %>%
  # filter(!(gameId %in% excludeIncomplete))
  filter()

sprintf('Incomplete games: %d', length(excludeIncomplete))
```

###Data transformation:
```{r datatransf, include=FALSE}
head(d %>% mutate(targetName = d$target$name) %>% 
       select(condition, targetName, directorFirstMessage, nameClickedObj))
```

**Overall accuracy:**
```{r ovv_accuracy, echo=FALSE}
toplot =  d %>%
  group_by(gameId) %>%
  summarise(Mean=mean(correct),CILow=ci.low(correct),CIHigh=ci.high(correct)) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(lowacc=ifelse(Mean<0.70,"1","0"))

h=0.70
ggplot(toplot, aes(x=reorder(gameId,Mean), y=Mean)) +
  geom_bar(stat="identity", fill="lightblue") +
  geom_hline(yintercept=h) +
  geom_text(aes(0, h, label=h, vjust=-1, hjust=-0.3)) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.25) +
  theme(axis.text.x=element_blank()) +
  ylab("Accuracy") +
  xlab("English speakers")

ggsave(file="viz/accuracy.pdf",width=5,height=3)
```

**Exclusion: Remove games with accuracy <70%: **
```{r exc_accuracy, echo=FALSE}
excludeAccuracy = toplot %>%
  filter(lowacc==1)
excludeAccuracy 

d = d[!(d$gameId %in% excludeAccuracy$gameId),]

sprintf("Games remaining after exclusion: %d", length(unique(d$gameId))) #46 games left
```

**Accuracy by trial type:**
```{r accuracy_tt, echo=FALSE}
toplot =  d %>%
  group_by(condition) %>%
  summarise(Mean=mean(correct),CILow=ci.low(correct),CIHigh=ci.high(correct)) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(lowacc=ifelse(Mean<0.70,"1","0"))

ggplot(toplot, aes(x=reorder(condition,Mean), y=Mean, fill = condition)) +
  geom_bar(position="dodge", stat="identity") +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.25, position=position_dodge(width = 0.9)) +
  theme(axis.text.x = element_text(angle=90),
        legend.position = "none") +
  ylab("Accuracy") +
  xlab("Trial type")
  

ggsave(file="viz/accuracy_trialType.pdf",width=6,height=4.5)
```

```{r}
# Was a color mentioned?
d$colorMentioned = ifelse(grepl("gray|grey|green|purple|white|black|brown|violet|yellow|gold|orange|silver|blue|pink|red", d$directorFirstMessage, ignore.case = TRUE), T, F)
table(d$colorMentioned)

# Was a size mentioned?
d$sizeMentioned = ifelse(grepl("big|small|bigger|smaller|tiny|huge|large|larger|little|biggest|smallest|largest", d$directorFirstMessage, ignore.case = TRUE), T, F)
table(d$sizeMentioned)

# Was the object's type (noun) mentioned?
d$typeMentioned = ifelse(grepl("avocado|balloon|cap|belt|bike|billiardball|binder|book|bracelet|bucket|butterfly|candle|chair|coat hanger|comb|cushion|guitar|flower|frame|golf ball|hair dryer|jacket|napkin|ornament|pepper|phone|rock|rug|shoe|stapler|tack|teacup|toothbrush|turtle|wedding cake|yarn", d$directorFirstMessage, ignore.case = TRUE), T, F)
table(d$typeMentioned)

# Was a bleached noun used?
d$oneMentioned = ifelse(grepl(" one|thing|item|object", d$directorFirstMessage, ignore.case = TRUE), T, F)
table(d$oneMentioned)

# Was an article used?
d$theMentioned = ifelse(grepl("the |a |an ", d$directorFirstMessage, ignore.case = TRUE), T, F)
table(d$theMentioned)

# Write this dataset for manual correction of typos like "pruple"
write_delim(data.frame(d %>%
                         select(-target, -images, -listenerImages, -speakerImages,
                                -chatLog, -gameChat)), 
            "../../data/englishPilot/preManualTypoCorrection.tsv", delim="\t")

# Read manually corrected dataset for further preprocessing
d = read_delim("../../data/englishPilot/preManualTypoCorrection.tsv", delim = "\t") %>%
  filter(grepl("color|size", condition)) %>%
  mutate(clickedFeatures = strsplit(nameClickedObj, "_"),
         clickedColor = map(clickedFeatures, pluck, 2),
         clickedSize = map(clickedFeatures, pluck, 1),
         clickedType = map(clickedFeatures, pluck, 3))

colsizerows = nrow(d)

# How many trials were automatically labelled as mentioning a pre-coded level of reference?
auto_trials = sum(d$automaticallyLabelledTrial)
print(paste("percentage of automatically labelled trials: ", auto_trials*100/colsizerows)) # 95.7 in Degen 2020

# How many trials were manually labelled as mentioning a pre-coded level of reference? (overlooked by grep search due to typos or grammatical modification of the expression)
manu_trials = sum(d$manuallyAddedTrials)
print(paste("percentage of manually added trials: ", manu_trials*100/colsizerows)) # 1.9 in Degen 2020

# How often were articles omitted?
no_article_trials = colsizerows - sum(d$theMentioned)
print(paste("percentage trials where articles were omitted: ", no_article_trials*100/colsizerows)) # 71.6 in Degen 2020

# How often were nouns omitted?
d$article_mentioned = ifelse(d$oneMentioned == TRUE | d$theMentioned == TRUE, 1, 0)
no_noun_trials = colsizerows - sum(d$article_mentioned)
print(paste("percentage of trials where nouns were omitted: ", no_noun_trials*100/colsizerows)) # 88.6 in Degen 2020

# In how many cases did the listener choose the wrong object?
print(paste(100*(1-(sum(d$correct)/colsizerows)),"% of cases of non-target choices")) # 1.5 in Degen 202

# How many unique pairs?
length(unique(d$gameId)) # 64

# Code for each trial: sufficient property, number of total distractors, number of distractors that differ on and that share insufficient dimension value with target
d$SufficientProperty = as.factor(ifelse(d$condition %in% c("size21", "size22", "size31", "size32", "size33", "size41", "size42", "size43", "size44"), "size", "color"))
d$RedundantProperty = ifelse(d$SufficientProperty == 'color',"size redundant","color redundant")
d$NumDistractors = ifelse(d$condition %in% c("size21","size22","color21","color22"), 2, ifelse(d$condition %in% c("size31","size32","size33","color31","color32","color33"),3,4))
d$NumDiffDistractors = ifelse(d$condition %in% c("size22","color22","size33","color33","size44","color44"), 0, ifelse(d$condition %in% c("size21","color21","size32","color32","size43","color43"), 1, ifelse(d$condition %in% c("size31","color31","size42","color42"),2,ifelse(d$condition %in% c("size41","color41"),3, 4))))
d$NumSameDistractors = ifelse(d$condition %in% c("size21","size31","size41","color21","color31","color41"), 1, ifelse(d$condition %in% c("size22","size32","size42","color22","color32","color42"), 2, ifelse(d$condition %in% c("size33","color33","size43","color43"),3,ifelse(d$condition %in% c("size44","color44"),4,NA))))
d$SceneVariation = d$NumDiffDistractors/d$NumDistractors
d$TypeMentioned = d$typeMentioned

# Add empirical typicality ratings
# Add color typicality ratings ("how typical is this color for a stapler?" wording)
typicalities = read.table("../../data/Degen2020_Typicality/typicality_exp1_colortypicality.csv",header=T)
head(typicalities)
typicalities = typicalities %>%
  group_by(Item) %>%
  mutate(OtherTypicality = c(Typicality[2],Typicality[1]),OtherColor = c(as.character(Color[2]),as.character(Color[1])))
typicalities = as.data.frame(typicalities)
row.names(typicalities) = paste(typicalities$Item,typicalities$Color)
d$ColorTypicality = typicalities[paste(d$clickedType,d$clickedColor),]$Typicality
d$OtherColorTypicality = typicalities[paste(d$clickedType,d$clickedColor),]$OtherTypicality
d$OtherColor = typicalities[paste(d$clickedType,d$clickedColor),]$OtherColor
d$TypicalityDiff = d$ColorTypicality-d$OtherColorTypicality  
d$normTypicality = d$ColorTypicality/(d$ColorTypicality+d$OtherColorTypicality)

# Add typicality norms for objects with modified and unmodified utterances ("how typical is this for a stapler?" vs "how typical is this for a red stapler?" wording)
typs = read.table("../../data/Degen2020_Typicality/typicality_exp1_objecttypicality.csv",header=T)
head(typs)
typs = typs %>%
  group_by(Item) %>%
  mutate(OtherTypicality = c(Typicality[3],Typicality[4],Typicality[1],Typicality[2])) 
typs = as.data.frame(typs)
row.names(typs) = paste(typs$Item,typs$Color,typs$Modification)
d$ColorTypicalityModified = typs[paste(d$clickedType,d$clickedColor,"modified"),]$Typicality
d$OtherColorTypicalityModified = typs[paste(d$clickedType,d$clickedColor,"modified"),]$OtherTypicality
d$TypicalityDiffModified = d$ColorTypicalityModified-d$OtherColorTypicalityModified  
d$normTypicalityModified = d$ColorTypicalityModified/(d$ColorTypicalityModified+d$OtherColorTypicalityModified)
d$ColorTypicalityUnModified = typs[paste(d$clickedType,d$clickedColor,"unmodified"),]$Typicality
d$OtherColorTypicalityUnModified = typs[paste(d$clickedType,d$clickedColor,"unmodified"),]$OtherTypicality
d$TypicalityDiffUnModified = d$ColorTypicalityUnModified-d$OtherColorTypicalityUnModified  
d$normTypicalityUnModified = d$ColorTypicalityUnModified/(d$ColorTypicalityUnModified+d$OtherColorTypicalityUnModified)

# Reduce dataset to target trials for visualization and analysis

# Exclude trials on which target wasn't selected
targets = d %>% filter(correct == 1)
nrow(targets) # 2138 cases in Degen 2020

# Categorize everything that isn't a size, color, or size-and-color mention as OTHER
targets$UtteranceType = as.factor(ifelse(targets$sizeMentioned & targets$colorMentioned, "size and color", ifelse(targets$sizeMentioned, "size", ifelse(targets$colorMentioned, "color","OTHER"))))

# examples of what people say when utterance is not clearly categorizable:
targets[targets$UtteranceType == "OTHER",]$directorFirstMessage

targets = droplevels(targets)
table(targets$UtteranceType)
table(targets[targets$UtteranceType == "OTHER",]$gameId) 
targets$Color = ifelse(targets$UtteranceType == "color",1,0)
targets$Size = ifelse(targets$UtteranceType == "size",1,0)
targets$SizeAndColor = ifelse(targets$UtteranceType == "size and color",1,0)
targets$Other = ifelse(targets$UtteranceType == "OTHER",1,0)
targets$Item = sapply(strsplit(as.character(targets$nameClickedObj),"_"), "[", 3)
targets$redUtterance = as.factor(ifelse(targets$UtteranceType == "size and color","redundant",ifelse(targets$UtteranceType == "size" & targets$SufficientProperty == "size", "minimal", ifelse(targets$UtteranceType == "color" & targets$SufficientProperty == "color", "minimal", "other"))))
targets$RatioOfDiffToSame = targets$NumDiffDistractors/targets$NumSameDistractors
targets$DiffMinusSame = targets$NumDiffDistractors-targets$NumSameDistractors

# Prepare data for Bayesian Data Analysis by collapsing across specific size and color terms
targets$redUtterance = as.factor(as.character(targets$redUtterance))
targets$CorrectProperty = ifelse(targets$SufficientProperty == "color" & (targets$Color == 1 | targets$SizeAndColor == 1), 1, ifelse(targets$SufficientProperty == "size" & (targets$Size == 1 | targets$SizeAndColor == 1), 1, 0)) # 20 cases of incorrect property mention
targets$minimal = ifelse(targets$SizeAndColor == 0 & targets$UtteranceType != "OTHER", 1, 0)
targets$redundant = ifelse(targets$SizeAndColor == 1, 1, 0)
targets$BDAUtterance = "size"#as.character(targets$clickedSize)
targets[targets$Color == 1,]$BDAUtterance = as.character(targets[targets$Color == 1,]$clickedColor)
targets[targets$SizeAndColor == 1,]$BDAUtterance = paste("size",targets[targets$SizeAndColor == 1,]$clickedColor,sep="_")
targets$redBDAUtterance = "size_color"
targets[targets$Color == 1,]$redBDAUtterance = "color"
targets[targets$Size == 1,]$redBDAUtterance = "size"
targets[targets$Other == 1,]$redBDAUtterance = "other"
targets$BDASize = "size"
targets$BDAColor = "color"
targets$BDAFullColor = targets$clickedColor
targets$BDAOtherColor = "othercolor"
targets$BDAItem = "item"

# Code non-sensical and "closest"/"Farthest" cases (BW: not sure what this is supposed to do)
targets[targets$redBDAUtterance != "other" & targets$CorrectProperty == 0,c("gameId","condition","nameClickedObj","directorFirstMessage")]
targets$WeirdCases = FALSE
targets[targets$redBDAUtterance != "other" & targets$CorrectProperty == 0  & !targets$gameId %in% c(),]$WeirdCases = TRUE

# Write Bayesian data analysis files (data and unique conditions)
write.csv(targets[targets$redBDAUtterance != "other" & targets$WeirdCases == FALSE,c("gameId","roundNumber","condition","BDASize","BDAColor","BDAOtherColor","BDAItem","redBDAUtterance")],file="../../data/englishPilot/bda_data.csv",quote=F,row.names=F)
write.csv(unique(targets[targets$redBDAUtterance != "other" & targets$WeirdCases == FALSE,c("BDAColor","BDASize","condition","BDAOtherColor","BDAItem")]),file="../../data/englishPilot/unique_conditions.csv",quote=F,row.names=F)

# Write file for regression analysis and visualization

dd = targets %>%
  filter(redUtterance != "other" & WeirdCases == FALSE) %>%
  rename(Trial=roundNumber, TargetItem=nameClickedObj, gameid = gameId,
         refExp = directorFirstMessage, speakerMessages = directorAllMessages,
         listenerMessages = guesserAllMessages) %>%
  mutate(clickedColor = as.character(clickedColor),
         clickedSize = as.character(clickedSize),
         clickedType = as.character(clickedType)) %>%
  select(gameid,Trial,TargetItem,UtteranceType,redUtterance,SufficientProperty,RedundantProperty,NumDistractors,NumSameDistractors,SceneVariation,speakerMessages,listenerMessages,refExp,minimal,redundant,clickedType,clickedSize,clickedColor,colorMentioned,sizeMentioned,typeMentioned,oneMentioned,theMentioned,ColorTypicality,OtherColorTypicality,OtherColor,TypicalityDiff,normTypicality,ColorTypicalityModified,ColorTypicalityUnModified,OtherColorTypicalityModified,OtherColorTypicalityUnModified,TypicalityDiffModified,normTypicalityModified,TypicalityDiffUnModified,normTypicalityUnModified) #alt1Name,alt1SpLocs,alt1LisLocs,alt2Name,alt2SpLocs,alt2LisLocs,alt3Name,alt3SpLocs,alt3LisLocs,alt4Name,alt4SpLocs,alt4LisLocs)
nrow(dd)

write_delim(dd, "../../data/englishPilot/data_exp1.tsv",delim="\t")

```